### 2015-11-16 thesis-proposal/problem.tex
Updated timeline

In the dissertation, I plan to first describe the simplest style of TSMs (i.e. unparameterized expression TSMs) by example. This is \textbf{complete}. I will next present a formal system that formalizes such TSMs. The account in Sec. \ref{sec:tsm-formalism} represents the first and most substantial step of this plan. A complete draft of this chapter, with the exception of proofs at the end, is \textbf{complete}. I plan to finish the proofs by \textbf{Nov. 19}. This system will serve as the basis for several extensions that capture other constructs described above, so I will ask the committee to read this section in detail once it is complete.

>>>>

In the dissertation, I plan to first describe the simplest style of TSMs -- unparameterized expression TSMs -- by example. This is \textbf{complete}. I will next present a formal system that captures such TSMs. The account in Sec. \ref{sec:tsm-formalism} represents the first and most substantial step of this plan. A complete draft of this chapter is \textbf{complete}. This system will serve as the basis for several extensions that capture other constructs described above, so I will ask the committee to read this section in detail once the proposal is complete.
